---
title: "Shiny Project - Customisable Plot for Random Normal Distribution"
author: "Gito"
date: "2024-11-15"
output: slidy_presentation
---

## Executive Summary

This Project is part of Coursera - John Hopkins on R Data Science Specialization with topic Shiny App and Reproducible Pitch.

I made Customisable Plot for Random Normal Distribution with customisable mean, standard deviation and number of samples with reactivity plot.

Below are the steps in creating shiny web app :

1.  2 files generated for ui.R and server.R and install necessary library
2.  ui.R file is user interface input to genarate the variables (mean, standard deviation and number of samples)
3.  server.R is plotting function

## User Interface File (ui.R)

UI page is managed by ui.R. I select page which consists of tabs and panel.

Tabs consists of main tab and documentation tab

Panel consists of input variable and plot.

Below are code to generate the ui.R \*\*\* The code might not be executed properly in presenation mode, you can see result on github page or rpub

```{r }
library(shiny)
library(rmarkdown)
rmdfile <- c("About.Rmd")
fluidPage(
    # Application title
    titlePanel("Normal Distibution Density Plot Generator with Customisable Mean, Standar Deviation and Number of Samples"),
    # Sidebar with a slider input for number of bins
    tabsetPanel(
      tabPanel("Main Page",
    sidebarLayout(
        sidebarPanel(
          helpText("Please select value wisely so you can see proper plot"),
          numericInput("randnum", "Please fill Number of Samples? Select > 1",
                       value = 10),
          numericInput("mean", "Please fill Mean",
                       value = 1),
          numericInput("sd", "Please fill Stdandar Deviation",
                       value = 2),
          sliderInput("xslider","Select X-axis Zoom with default value -100 to 100",
                        min = -100,max = 100,value = c(-10,10)),
          submitButton("Submit to Plot")
        ),
        # Show a plot of the generated distribution
        mainPanel(
            plotOutput("plot1")
        )
    )
), tabPanel("Documentation/About",
            mainPanel(
              includeMarkdown("About.Rmd")
            ))
)
)
```

## Server File (server.R)

Server file is used to manage plot function.

```{r }
library(shiny)
# Define server logic required to draw a histogram
function(input, output, session) {
    output$plot1 <- renderPlot({
        # generate bins based on input$bins from ui.R
        x    <- rnorm(input$randnum,input$mean,input$sd)
        xd <- density(x)
        plot(xd,xlim = c(input$xslider[1],input$xslider[2]),
             main = "Density Chart",
             xlab = "Value",ylab = "Density",
             col = "blue",lwd = 4)
    })
}
```

## Documentation

Documentation and result can be found on below github and rpub links
